---
title: "Task1"
author: "Dola Anna"
date: "10/01/2024"
format:
  html:
    embed-resources: true
editor: source
---

## Question 1

Question description
1. Create variables with all atomic types. Atomic types: `character`, `numeric`, `integer`, `complex`, `logical`.
```{r}
# code for solving task
v1 <- 56.87767467
v2 <- 76L
v3 <- "have a good day"
v4 <- TRUE
v5 <- 26+8i
print(c(v1,v2,v3,v4,v5))
```


## Question 2 

Question description
2. Create the next vectors:
  * sequence from 5 to 75;
  * numbers: 3.14, 2.71, 0, 13;
  * with 100 `TRUE` values.
```{r}
# code for solving task
sequence_vector <- 5:75
number_vector <- c(3.14,2.71,0.13)
true_vector <- rep(TRUE,100)

sequence_vector
number_vector
true_vector
```

## Question 3

Question description
3. Create the next matrix:

|  |   |  |
|:---:|:-----:|:---:|
| 12  | 34    | 87  |
| -12 | -12.1 | 0   |
| 3.6 | 0.5   | 1.3 |
```{r}
# code for solving task
my_data <- matrix(c(12, 34, 87, -12, -12.1, 0, 3.6, 0.5, 1.3), nrow = 3, byrow = TRUE)
print(my_data)
```

## Question 4
Question description
4. Create a `list` with all atomic types.
```{r}
# code for solving task
my_list <- list(
  integer_value = 75L,
  numeric_value = 5.43,
  character_value = "Have a good day",
  logical_value = TRUE,
  complex_value = 2+4i
)

my_list
```

## Question 5
Question description
5. Create a `factor` with 3 levels: `infant`, `child`, `adult`.
```{r}
# code for solving task
my_factor <- factor(c("big","avarage","small","small","avarage","big"),
levels = c("big","avarage","small"))
my_factor
```

## Question 6
Question description
6. Create a `data frame`
```{r}
# code for solving task
age_factor <- factor(c("infant","child","adult"), levels = c("infant","child","adult"))

print(age_factor)
```

## Question 7
Question description
7. Change column names of the `data frame`.
```{r}
# code for solving task
# Sample Data Frame
data <- data.frame(
  A = c(1, 2, 3),
  B = c(4, 5, 6),
  C = c(7, 8, 9)
)

# Display original Data Frame
cat("Original Data Frame:\n")
print(data)

# Change column names
new_column_names <- c("Column1", "Column2", "Column3")
colnames(data) <- new_column_names

# Display modified Data Frame
cat("\nData Frame with Changed Column Names:\n")
print(data)

```

